---
title: "16 Clusters Analysis"
output:
  html_document:
    df_print: paged
---

Loading library
```{r}
library(Seurat)
library(dplyr)
library(ggplot2)
library(cowplot)
```

Load gene names
```{r}
  id2symbol <- read.table("data/id2symbol.txt",header=T,sep="\t",quote="\"", stringsAsFactors=F)
#Seurat V3 symbol replace "_" with "-"
  id2symbol$symbol <- gsub(pattern = "_", replacement = "-", x = id2symbol$symbol)
  mito_gene <- paste("Xe_0",23787:23800,sep="")
  mito_gene <- id2symbol[id2symbol$ID %in% mito_gene,]$symbol
```

Load Seurat object for each sample
```{r}
stalk <- readRDS("data/stalk.RDS")
tentacle <- readRDS("data/tentacle.RDS")
whole <- readRDS("data/whole.RDS")
whole_v3 <-readRDS("data/whole_v3.RDS")
```

Align non-regeneration samples by Seurat3
```{r}
combined.list <- list()
combined.list[["whole"]] <- whole
combined.list[["tentacle"]] <- tentacle
combined.list[["stalk"]] <- stalk
combined.list[["whole_v3"]] <- whole_v3
combined.anchors <- FindIntegrationAnchors(object.list = combined.list, anchor.features =1000, dims = 1:20)
combined.integrated <- IntegrateData(anchorset = combined.anchors, dims = 1:20,features.to.integrate = id2symbol$symbol)
DefaultAssay(combined.integrated) <- "integrated"

# Run the standard workflow for visualization and clustering
combined.integrated <- ScaleData(combined.integrated, verbose = FALSE,features =id2symbol$symbol)
combined.integrated <- RunPCA(combined.integrated, npcs = 20, verbose = FALSE)
combined.integrated <- RunTSNE(combined.integrated, reduction = "pca", dims = 1:20)

combined.integrated <- FindNeighbors(object = combined.integrated,dims = 1:20)
combined.integrated <- FindClusters(combined.integrated,resolution = 0.19,algorithm =1, group.singletons = F)
xenia <- combined.integrated
rm(combined.integrated)
```



Identify markers for each cluster and Plot heatmap
```{r}
xenia@meta.data$seurat_clusters <- as.numeric(as.character(xenia@meta.data$seurat_clusters))+1
Idents(xenia)<- "seurat_clusters"
xenia@active.ident <- factor(x = xenia@active.ident, levels = 1:16)

DimPlot(xenia, reduction = "tsne", label=T)

xenia.markers<- FindAllMarkers(xenia, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
xenia.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
xenia@meta.data[,"seurat_clusters",drop=FALSE] %>% add_rownames() %>% group_by(seurat_clusters) %>% sample_n(40) -> index

DoHeatmap(xenia, features = top10$gene,label=F)
DoHeatmap(xenia, features = top10$gene,label=F,cells=index$rowname)

xenia.markers <- xenia.markers[xenia.markers$p_val_adj<0.05,]
saveRDS(xenia.markers,"data/cluster_markers.RDS")
saveRDS(xenia,"data/non_regeneration_integrated.RDS")

```
Marker specificity
We define that a gene is enriched in a cell if the expression of the gene in the cell is higher than the average expression of the gene among all cells. 
We further define the specificity of a marker gene in a cluster as the percentage of cells , in which the marker gene is enriched as defined above within the cluster.
```{r}
exp <- xenia@assays$integrated@data
exp_spcificity <- exp >Matrix::rowMeans(exp)
temp_list <- list()
for (i in 1:16){
  sub_cluster <- xenia.markers[xenia.markers$cluster ==i,]
  marker_exp <- exp_spcificity[xenia.markers[xenia.markers$cluster ==i,]$gene,]
  spcificity_within_cluster <- Matrix::rowSums(marker_exp[,colnames(marker_exp) %in% rownames(xenia@meta.data[xenia@meta.data$seurat_clusters == i,])])/sum(xenia@meta.data$seurat_clusters == i)
  spcificity_outside_cluster <- Matrix::rowSums(marker_exp[,colnames(marker_exp) %in% rownames(xenia@meta.data[!xenia@meta.data$seurat_clusters == i,])])/sum(!xenia@meta.data$seurat_clusters == i)
  temp <- data.frame(gene=rownames(marker_exp),spcificity_within_cluster=spcificity_within_cluster,spcificity_outside_cluster=spcificity_outside_cluster)
  sub_cluster <- left_join(sub_cluster, temp)
  temp_list[[i]]<-sub_cluster
}
xenia.markers<- do.call(rbind,temp_list)
#Filter low specificity markers
xenia.markers <- xenia.markers[xenia.markers$spcificity_within_cluster>0.5,]
saveRDS(xenia.markers,"data/cluster_markers.RDS")
```


violin plot of cnidocyte markers
```{r}
gene2plot <- c("Galactose binding lectin domain-2","Galactose binding lectin domain-3","Galactose binding lectin domain-4","Xe-028815" ,"Xe-001210")
VlnPlot(object =xenia, features = gene2plot, pt.size= 0,combine = F,assay = "RNA") 


```


Cnidocytes subcluster
```{r}

cnidocyte <- SubsetData(xenia, subset.name = "seurat_clusters", accept.value =11) 
cnidocyte <- RunTSNE(cnidocyte, reduction = "pca", dims = 1:10)
cnidocyte <- FindNeighbors(object = cnidocyte,dims = 1:10)
cnidocyte <- FindClusters(cnidocyte,resolution = 0.05,algorithm =1, group.singletons = F)

cnidocyte<- RenameIdents(cnidocyte, "0" = "11-1")
cnidocyte<- RenameIdents(cnidocyte, "1" = "11-2")
p2 <- list()
p2[[1]] <- DimPlot(cnidocyte, reduction = "tsne", label=F,cols=c("#57a0ff","#ff9757"))
p2[[2]] <-FeaturePlot(cnidocyte,features=c("Galactose binding lectin domain-3"),blend = F,reduction = "tsne",cols =c("grey","red"))
p2[[3]] <-FeaturePlot(cnidocyte,features=c("Xe-028815"),blend = F,reduction = "tsne",cols =c("grey","red"))
  
# Visualization

p2[[1]] <- DimPlot(cnidocyte, reduction = "tsne", label=F,cols=c("#57a0ff","#ff9757")) + NoLegend()
p2[[2]] <- FeaturePlot(cnidocyte, id2symbol[id2symbol$ID %in% c("Xe_028815"),]$symbol,cols = c("grey","red"),reduction="tsne")+ NoLegend()

p2[[3]] <- FeaturePlot(cnidocyte, id2symbol[id2symbol$ID %in% c("Xe_006066"),]$symbol,cols = c("grey","red"),reduction="tsne")+ NoLegend() +ggtitle("Xe_006066")



plot_grid(p2[[1]],p2[[2]],p2[[3]],nrow = 1)




```
```{r}
cnidocyte.markers<- FindAllMarkers(cnidocyte, only.pos = TRUE, min.pct = 0.25, thresh.use = 0.25)
cnidocyte.markers %>% group_by(cluster) %>% top_n(10, avg_logFC) -> top10
cnidocyte@meta.data[,"integrated_snn_res.0.05",drop=FALSE] %>% add_rownames() %>% group_by(integrated_snn_res.0.05) %>% sample_n(40) -> index

DoHeatmap(cnidocyte, features = top10$gene,label=F)
DoHeatmap(cnidocyte, features = top10$gene,label=F,cells=index$rowname)
```


SessionInfo
```{r}
sessionInfo()
```

