```{r}
library(Seurat)
library(dplyr)
library(ggplot2)

library(velocyto.R)
```
#define function
```{r}
velocity_analysis <- function(seurat,kCells=10,reduction="tsne",grid.n=50,scale=1,arrow.scale=8)
{
  # take embedding from the Seurat data object
  emb <- seurat@reductions[reduction][[1]]@cell.embeddings
  emb <- emb[,1:2]
  emat <- emat[,colnames(emat) %in% rownames(emb)]
  nmat <- nmat[,colnames(nmat) %in% rownames(emb)]
  # Estimate the cell-cell distances 
  cell.dist <- as.dist(1-armaCor(t(x = Embeddings(object = seurat, reduction = "pca"))))
  
  fit.quantile <- 0.02
  
  # Main velocity estimation
  rvel.cd <- gene.relative.velocity.estimates(emat,nmat,deltaT=2,kCells=kCells,cell.dist=cell.dist, fit.quantile=fit.quantile, n.cores=12)
  
  
 gg <- DimPlot(seurat, reduction = reduction) +scale_color_manual(values=c("green","red","grey"))
  colors <- as.list(ggplot_build(gg)$data[[1]]$colour)
  names(colors) <- rownames(emb)
  show.velocity.on.embedding.cor(emb*scale,rvel.cd,n=30,scale='sqrt',
                                 cell.colors=ac(colors,alpha=0.5),
                                 cex=0.8,arrow.scale=arrow.scale,show.grid.flow=T,
                                 min.grid.cell.mass=1.0,grid.n=grid.n,arrow.lwd=1,
                                 do.par=F,cell.border.alpha = 0.1,
                                 n.cores=12,main="Cell Velocity")
}

AddReads <- function (loomfile,sample){
ldat2 <- read.loom.matrices(loomfile)
emat2 <- ldat2$spliced
nmat2 <- ldat2$unspliced
colnames(emat2)<-paste(substring(colnames(emat2),28,43),sample,sep="")
colnames(nmat2)<-paste(substring(colnames(nmat2),28,43),sample,sep="")
emat <<- cbind(emat,emat2)
nmat <<- cbind(nmat,nmat2)
}
```

Splicing Matrix for RNAvelocity
```{r}
ldat <- read.loom.matrices("/mnt/sequence/mhu2/git/mhu2-xelongata/scRNA/wrap_up/data/Reg4d_v3/possorted_genome_bam_UQCW6.loom")
emat <- ldat$spliced
nmat <- ldat$unspliced
colnames(emat)<-paste(substring(colnames(emat),28,43),"reg4d_v3",sep="")
colnames(nmat)<-paste(substring(colnames(nmat),28,43),"reg4d_v3",sep="")
AddReads(loomfile="/mnt/sequence/mhu2/git/mhu2-xelongata/scRNA/wrap_up/data/reg4d/possorted_genome_bam_71VGW.loom",sample="reg4d")
```
unsplicing and splicing reads comparison
```{r}
splice_matrix <- t(rbind(Matrix::colSums(emat),Matrix::colSums(nmat)))
colnames(splice_matrix) <- c("spliced","unspliced")
splice_matrix <- as.data.frame(splice_matrix)
splice_matrix$sample <- substring(rownames(splice_matrix),17,24)
splice_matrix$unspliced_ratio <- splice_matrix$unspliced/(splice_matrix$spliced+splice_matrix$unspliced)
splice_matrix$identity <- rownames(splice_matrix)

splice_matrix %>% group_by(sample) %>% summarise(unspliced_ratio = mean(unspliced_ratio))
ggplot(data=splice_matrix[splice_matrix$sample %in% c("reg4d","reg4d_v3"),])+geom_density(aes(x=unspliced_ratio,color=sample))
```

```{r}
reg4d_v3 <- readRDS("data/reg4d_v3.RDS")
reg4d_v3@meta.data$orig.ident <- rownames(reg4d_v3@meta.data)

xenia <- readRDS("data/non_regeneration_integrated.RDS")
reg4d.anchors <- FindTransferAnchors(reference = xenia, query = reg4d_v3, 
    dims = 1:30)
predictions <- TransferData(anchorset = reg4d.anchors, refdata =as.character(xenia$seurat_clusters), 
    dims = 1:30)
reg4d_v3 <- AddMetaData(reg4d_v3, metadata = predictions)
```


```{r}
reg4d_v3 <- ScaleData(reg4d_v3, verbose = FALSE)
reg4d_v3 <- RunPCA(reg4d_v3, npcs = 30, verbose = FALSE)
reg4d_v3@meta.data <- left_join(reg4d_v3@meta.data,splice_matrix[,c("identity","unspliced_ratio")],by=c("orig.ident"="identity"))
rownames(reg4d_v3@meta.data) <- reg4d_v3@meta.data$orig.ident
#As in the RNA velocity paper mentioned, 15–25% of reads contained unspliced intronic sequences.  While in xenia, the unspliced reads percentage is lower. This is more severe when we carried out scRNA with 10x v3 chemical. As unspliced intronic sequences was used for cell feature fate prediction, we filter out cells with less than 10% unspliced reads and use remained cells for RNA velocity analysis.
reg4d_v3_filterd <- reg4d_v3[,rownames(reg4d_v3@meta.data[reg4d_v3@meta.data$unspliced_ratio>0.1,])]
reg4d_v3_filterd<- RunTSNE(reg4d_v3_filterd, reduction = "pca", dims = 1:25)
DimPlot(reg4d_v3_filterd,reduction = "tsne",group.by = "predicted.id",label = T)
velocity_analysis(reg4d_v3_filterd,kCells=2,reduction="tsne",scale = 0.3)
```


Define early and late endo-symbiotic cell in reg4d_v3 sample
```{r}
temp <-reg4d_v3_filterd@reductions$tsne@cell.embeddings
temp <- as.data.frame(as.matrix(temp))
temp$seurat_clusters <- reg4d_v3_filterd@meta.data$predicted.id

temp$symbiotic <- "Other"
temp[temp$seurat_clusters ==16 & temp$tSNE_2 < -20 & temp$tSNE_1 >5, ]$symbiotic <- "Late symbiotic"
temp[temp$tSNE_1 <18.5 & temp$tSNE_2 < -20 & temp$seurat_clusters ==16, ]$symbiotic <- "Early symbiotic"
temp$symbiotic <- factor(temp$symbiotic,levels = c("Early symbiotic","Late symbiotic","Other"))
reg4d_v3_filterd@meta.data$symbiotic <- temp$symbiotic
```

```{r}
Idents(reg4d_v3_filterd) <- "symbiotic"

#set scale to 0.3 to fit the RNA velocity space
velocity_analysis(reg4d_v3_filterd,kCells = 2,reduction = "tsne",scale = 0.3,arrow.scale = 15)

```

reg4d v2 chemical RNA velocity
```{r}
reg4d <- readRDS("data/reg4d.RDS")

reg4d.anchors <- FindTransferAnchors(reference = xenia, query = reg4d, 
    dims = 1:30)
predictions <- TransferData(anchorset = reg4d.anchors, refdata =as.character(xenia$seurat_clusters), 
    dims = 1:30)
reg4d <- AddMetaData(reg4d, metadata = predictions)
reg4d <- ScaleData(reg4d, verbose = FALSE)
reg4d <- RunPCA(reg4d, npcs = 30, verbose = FALSE)
```

```{r}
reg4d <- RunTSNE(reg4d, reduction = "pca", dims = 1:15)
reg4d@meta.data$orig.ident <- rownames(reg4d@meta.data)
DimPlot(reg4d_v3_filterd,reduction = "tsne",group.by = "predicted.id",label = T)
velocity_analysis(reg4d,kCells = 2,reduction = "tsne",arrow.scale = 15)
```


Define early and late symbiotic in V2 chemical
```{r}
temp <-reg4d@reductions$tsne@cell.embeddings
temp <- as.data.frame(as.matrix(temp))
temp$seurat_clusters <- reg4d@meta.data$predicted.id
temp$symbiotic <- "Other"
temp[temp$seurat_clusters ==16, ]$symbiotic <- "Late symbiotic"
temp[ temp$tSNE_2 < 10.2 & temp$seurat_clusters ==16, ]$symbiotic <- "Early symbiotic"
temp$symbiotic <- factor(temp$symbiotic,levels = c("Early symbiotic","Late symbiotic","Other"))
reg4d@meta.data$symbiotic <- temp$symbiotic
```
```{r}
Idents(reg4d) <- "symbiotic"
velocity_analysis(reg4d,kCells = 2,reduction = "tsne",arrow.scale = 15)
```
Combine early and late symbiotic information from both sample and used later for monocle pseudotime analysis
```{r}
symbiotictic_velocity <- rbind(reg4d@meta.data[,c("orig.ident","symbiotic")],reg4d_v3_filterd@meta.data[,c("orig.ident","symbiotic")])
saveRDS(symbiotictic_velocity,"data/symbiotic_velocity.RDS")
```


save combined regeneration object for later use
```{r}
reg4d.list <- list(reg4d=reg4d,reg4d_v3=reg4d_v3)
reg4d.anchors <- FindIntegrationAnchors(object.list = reg4d.list, dims = 1:30)
reg4d.integrated <- IntegrateData(anchorset = reg4d.anchors, dims = 1:30)
xenia <- readRDS("data/non_regeneration_integrated.RDS")
reg4d.anchors <- FindTransferAnchors(reference = xenia, query = reg4d.integrated, 
    dims = 1:30)
predictions <- TransferData(anchorset = reg4d.anchors, refdata =as.character(xenia$seurat_clusters), 
    dims = 1:30)
reg4d.integrated <- AddMetaData(reg4d.integrated, metadata = predictions)
Idents(reg4d.integrated) <-"predicted.id"
saveRDS(reg4d.integrated,"data/reg4d.integrated.RDS")
```


